A thesis draft

### 2018-11-07 res/sections/79-Conclusions.tex
Finalized conclusions

In this thesis we have seen an ETSI MANO implementation proposal. We have 
described the technological components needed to build it, and we have 
presented the requirements of the whole implementations. Then we described 
the challenges we have encountered and how we solved it, taking choises 
valuating the pros and cons.

Finally, we corroborated our implementation with test, showing that a 
containerized approach is faster and more reliable thant a virtualized one

>>>>

In this thesis we have seen an ETSI MANO and RFC 7665 implementation proposal. 
We have described the technological components needed to build it, and we have 
presented the requirements of the whole implementation. Then we described 
the challenges we have encountered and how we solved it, taking choises 
valuating their pros and cons.

Finally, we corroborated our implementation with tests, showing that a 
containerized approach is faster and more reliable thant a virtualized one,
and illustrating that latency in communications through SFCs, while there 
is room for improvement, are decent considered the testbed environment.

In conclusion, we can say that the ETSI MANO specification, coupled with the 
RFC 7665 proposal and the new virtualization technologies avaiable in the 
market could change the shape of future mobile communications, leading to the 
creation of a 5G able to saddisfy the challenges of the present, such as IoT 
communications, media streaming, and real-time data, with the challenges of the 
future, as smart dust emerges as the next possible innovation.
